---
title: "R Notebook"
output: html_notebook
---

The goal here is instead of assuming everything is a power law, I'll use a gam to interpolate each size bin.
Then we do the generally same analysis.

```{r}
library(tidyverse)
library(tidyselect)
pass <- function(x){x}
#source("Remin_Library.R")
source("ModelStuff.R")
```

Data from elsewhere
```{r, message= FALSE}
options(readr.default_locale=readr::locale(tz="Mexico/General"))
source("UVP_2017_library.R")

ES01 <- read_csv("dataOut/binned_EachSize.csv") %>% filter(depth <= 1000)
DS01 <- read_csv("dataOut/binned_DepthSummary.csv") %>% filter(depth <= 1000)
twinS <- list(ES01, DS01)
```

```{r}
SimpleBins <- seq(from = 0, to = 1100, by = 50) # Modified the By

#debug(bin_depths)
#binnedS <- bin_depths(twinS, bins = SimpleBins) %>% calc_psd
binnedS <- bin_depths(twinS, bins = BianchiBins) %>% calc_psd

ESS <- binnedS[[1]]
DSS <- binnedS[[2]]
```

24 November 2020



```{r}
# I think I want to family gamma this if it goes negative; or maybe bust poisson back out



S43data <- ESS %>% filter(profile == "stn_043", depth <= 1000)

S43GAM2X <- S43data %>% my_double_gam
summary(S43GAM2X)
```

```{r}
S43dataEx <- expand_with_gam(S43data, S43GAM2X)
```

```{r}
nnp_size_ggplot_2d(S43dataEx)
gam_size_ggplot_2d(S43dataEx)
```




Order of operations
(1) recalculate things that need to be recalculated (like flux and what not)
(2) calculate disaggregation

# Recalculating

I should make the following code blocks into one function...
```{r}
S43Smooth <- S43dataEx %>%
  select(profile:vol, depth, n_nparticles = resp_fit) %>%
  mutate(nparticles = n_nparticles * binsize, TotalParticles = nparticles * vol)

S43Twin <- S43Smooth %>% make_twin_df_list() %>%
  calc_particle_parameters()

Esmooth42 <- S43Twin[[1]]
Dsmooth42 <- S43Twin[[2]]
```

```{r}
specData42 <- Esmooth42 %>% select(profile, depth, lb, nparticles, n_nparticles, flux_fit) %>%
  #mutate(sizeFlux = nnp * C_f_global * lb_vec * ag_global) %>%
  nest(spec_meta = c(lb, nparticles, n_nparticles, flux_fit))
```

```{r}
Dsmooth42_prepaired <- Dsmooth42 %>% left_join(specData42, by = c("profile", "depth")) %>%
   mutate(spec_only = map(spec_meta, ~pull(., nparticles))) %>% 
  # mutate(flux2 = map(spec_meta, ~summarize(., flux3 = sum(sizeFlux)))) %>%
  mutate(spec_prev = lag(spec_only),
         flux_prev = lag(tot_flux),
         DF = flux_prev - tot_flux,
         DFP = 1 - DF/flux_prev
         )
```

```{r}
shuffle_tune(Dsmooth42_prepaired$DFP[[5]], Dsmooth42_prepaired$spec_only[[5]], Dsmooth42_prepaired$DFP[[5]])

```

```{r}
# debugging
Dsmooth42_prepaired$DFP[[5]]
optFun(Dsmooth42_prepaired$spec_only[[5]], Dsmooth42_prepaired$DFP[[5]])
```

```{r}
# debugging
shuffle_tune(optFun(Dsmooth42_prepaired$spec_only[[5]], Dsmooth42_prepaired$DFP[[5]]), Dsmooth42_prepaired$spec_only[[5]], Dsmooth42_prepaired$DFP[[5]])

remin_smooth_shuffle(Dsmooth42_prepaired$spec_only[[5]], optFun(Dsmooth42_prepaired$spec_only[[5]], Dsmooth42_prepaired$DFP[[5]]))
remin_smooth_shuffle(Dsmooth42_prepaired$spec_only[[5]], Dsmooth42_prepaired$DFP[[5]])
```

```{r}
Dsmooth42_fixDFP <- Dsmooth42_prepaired %>%
  mutate(use_this_DFP = map2_dbl(spec_prev, DFP, optFun))
```

Testing what is going on with these spectra

```{r}
testDepth = 137.5
test_prev <- Dsmooth42_fixDFP %>% filter(depth == testDepth) %>% pull(spec_prev) %>% .[[1]]
test_spec <- Dsmooth42_fixDFP %>% filter(depth == testDepth) %>% pull(spec_only) %>% .[[1]]
test_DFP <- Dsmooth42_fixDFP %>% filter(depth == testDepth) %>% pull(DFP)
test_use_DFP <- Dsmooth42_fixDFP %>% filter(depth == testDepth) %>% pull(use_this_DFP)
test_spec
test_DFP
test_use_DFP

test_shuf <- remin_smooth_shuffle(test_prev, test_use_DFP)
test_shuf

optFun(test_prev, test_DFP)

shuffle_tune(test_use_DFP, test_prev, test_DFP)
```

```{r}
sum(test_prev * C_f_global * lb_vec ^ ag_global)
sum(test_spec * C_f_global * lb_vec ^ ag_global)
sum(test_shuf * C_f_global * lb_vec ^ ag_global)
```

test shuf's flux should equal test_spec's flux...

```{r}
Dsmooth42_remineralized <- Dsmooth42_fixDFP %>% .[-1,] %>%
  mutate(spec_pred = map2(spec_prev, use_this_DFP, remin_smooth_shuffle))
```

Runs as written. Lets do calcs later.

```{r}
Dsmooth42_concise <- Dsmooth42_remineralized %>% 
  mutate(spec_meta = map2(spec_meta, spec_prev, ~tibble(.x, np_prev = .y))) %>%
  mutate(spec_meta = map2(spec_meta, spec_pred, ~tibble(.x, np_pred = .y))) %>%
  select(profile, time, depth, DF, DFP, spec_meta)

Dsmooth42_unnest <- Dsmooth42_concise %>% unnest(spec_meta)
Dsmooth42_unnest
```

Examine change
```{r}

Dsmooth42_unnest %>% filter(depth == testDepth) %>% ungroup() %>% select(lb, nparticles, np_prev, np_pred) %>% pivot_longer(cols = c(nparticles, np_prev, np_pred)) %>% 
  ggplot(aes(x = lb, y = value, col = name)) + geom_point() + scale_x_log10() + scale_y_log10() + scale_color_manual(values = c("red", "blue", "gray20"))

# Dsmooth42_unnest %>% filter(depth == 625) %>% ungroup() %>% select(lb, nparticles, np_prev, np_pred) %>% pivot_longer(cols = c(nparticles, np_prev, np_pred)) %>% 
#   ggplot(aes(x = lb, y = value, col = name)) + geom_point(alpha = 0.75, size = 1) + scale_x_log10() + scale_y_log10() + scale_color_manual(values = c("red", "blue", "gray20"))

```
This doesn't look right.

```{r}
f_vec = C_f_global * lb_vec ^ ag_global

Dsmooth42_unnest %>% filter(depth == testDepth) %>% ungroup() %>% select(lb, nparticles, np_prev, np_pred) %>% pivot_longer(cols = c(nparticles, np_prev, np_pred)) %>% 
  ggplot(aes(x = lb, y = value * C_f_global * lb  ^ ag_global, col = name)) + geom_point() + scale_x_log10() + scale_y_log10() + scale_color_manual(values = c("red", "blue", "gray20"))
```


```{r}
# what is going on with my keyboard
Dsmooth42_sr02 <- Dsmooth42_unnest %>% 
  mutate(flux_prev = np_prev * f_vec,
         flux_pred = np_pred * f_vec,
         flux2 = nparticles * f_vec)
Dsmooth42_sr02_Tot <- Dsmooth42_sr02 %>% group_by(depth) %>%
  summarize(DF = first(DF), DFP = first(DFP),
            Flux = sum(flux2), Flux_Prev = sum(flux_prev), Flux_Pred = sum(flux_pred))
Dsmooth42_sr02_Small <- Dsmooth42_sr02 %>%
  filter(lb <= 0.53) %>%
  group_by(depth) %>%
  summarize(Flux = sum(flux2), Flux_Prev = sum(flux_prev), Flux_Pred = sum(flux_pred))

Dsmooth42_sr02_Big <- Dsmooth42_sr02 %>%
  filter(lb > 0.53) %>%
  group_by(depth) %>%
  summarize(Flux = sum(flux2), Flux_Prev = sum(flux_prev), Flux_Pred = sum(flux_pred))

Dsmooth42_sr02_All <- Dsmooth42_sr02_Tot %>%
  left_join(Dsmooth42_sr02_Small, by = "depth", suffix = c("", "_Small")) %>%
  left_join(Dsmooth42_sr02_Big, by = "depth", suffix = c("", "_Big"))  %>%
  mutate(osps = Flux_Small - Flux_Pred_Small, Disag = osps/DF) %>%
  mutate(obpb = Flux_Pred_Big - Flux_Big) # should equal osps, but doesn't
```

```{r}
Dsmooth42_sr02_All
```

```{r}
Dsmooth42_sr02_All %>% ggplot(aes(x = DFP, y = depth)) + scale_y_reverse() + geom_point()
```

```{r}
Dsmooth42_sr02_All %>% #filter(DFP <= 1) %>%
  ggplot(aes(y = depth, x = pracma::nthroot(DF, 3))) + geom_point() +
  scale_y_reverse()

Dsmooth42_sr02_All %>% #filter(DFP <= 1) %>%
  ggplot(aes(y = depth, x = pracma::nthroot(DFP, 1))) + geom_point() +
  scale_y_reverse()

Dsmooth42_sr02_All %>% #filter(DFP <= 1) %>%
  ggplot(aes(x = depth, y = Flux, 1)) + geom_point() +
  scale_x_log10() + scale_y_log10()
```

```{r}
Dsmooth42_sr02_All %>% filter(DFP <= 1) %>%
  ggplot(aes(y = depth, x = pracma::nthroot(osps, 3))) + geom_point() +
  scale_y_reverse()

Dsmooth42_sr02_All %>% filter(DFP <= 1) %>%
  ggplot(aes(y = depth, x = pracma::nthroot(Disag, 3))) + geom_point() +
  scale_y_reverse()
```

Still bizzare. Was running wrong code file. Works now.
Ok. And the disaggregation happens where the zoops go at night.

To do. 
* Finer bins. 
* Whole pipeline with different alpha and gamma params. Is this sensitive to those?
* Dry and reproducable code
* What is the particle size distribution of the new particles that is appearing in the mid water column and how do they compare to the particles that are appearing at the surface?

```{r}
sessionInfo()
```
