---
title: "R Notebook"
output: html_notebook
---
# CTD Data for comparason

```{r}
source("bring_in_ctd.R")
```

```{r}
library(tidyverse)
library(plotly)
library(cowplot)
```


```{r}
PhoticBase <- 160
OMZBase <- 900
OMZTop <- 90
```


```{r}
ctdP2 <- ctd.m %>% left_join(cast2 %>% select(pstation, cast), by = 'cast') %>% filter(pstation == 'P2')
# bin by 10 m
depthBins <- seq(from = 0, to = max(ctdP2$depth), by = 1)
depthMids <- seq(from = 1, to = max(ctdP2$depth), by = 1)
ctdP2$depthBin <- cut(ctdP2$depth, breaks = depthBins, labels = depthMids) %>% as.character %>% as.numeric
ctdP2Binned <- ctdP2 %>% filter(is.finite(depthBin)) %>% group_by(cast, variable, depthBin) %>% summarise(value = mean(value)) #%>% group_by(variable, depthBin) %>% summarize(value = mean(value))
```

```{r}
depthBins <- seq(from = 0, to = max(ctdP2$depth), by = 5)
depthMids <- seq(from = 1, to = max(ctdP2$depth), by = 5)
ctdP2$depthBin <- cut(ctdP2$depth, breaks = depthBins, labels = depthMids) %>% as.character %>% as.numeric
ctdP2BinnedCourse <- ctdP2 %>% filter(is.finite(depthBin)) %>% group_by(cast, variable, depthBin) %>% summarise(value = mean(value)) #%>% group_by(variable, depthBin) %>% summarize(value = mean(value))
```


Variability in fluorescence
```{r}
ctdP2Binned %>% filter(variable == "fluorescence") %>%
  ggplot(aes(y = depthBin, x = value, colour = as.ordered(cast))) +
  geom_path() + scale_y_reverse(limits = c(400, 0))
```

Mean Fluorescence
```{r}
fluprof <- ctdP2Binned %>% filter(variable == "fluorescence") %>%
  group_by(depthBin) %>% summarize(value = mean(value)) %>%
  ggplot(aes(y = depthBin, x = value)) +
  geom_path() + scale_y_reverse()
fluprof + scale_y_reverse(limits = c(400, 0))
```

Variability in Oxygen
```{r}
ctdP2Binned %>% filter(variable == "oxygen") %>%
  ggplot(aes(y = depthBin, x = value, colour = as.ordered(cast))) +
  geom_path() + scale_y_reverse()
```

Oxygen

```{r}
oxyprof <- ctdP2Binned %>% filter(variable == "oxygen") %>%
  group_by(depthBin) %>% summarize(value = mean(value)) %>%
  ggplot(aes(y = depthBin, x = value)) +
  geom_path() + scale_y_reverse()
oxyprof
```

```{r}
oxyprof <- ctdP2Binned %>% filter(variable == "oxygen") %>%
  group_by(depthBin) %>% summarize(value = mean(value)) %>%
  ggplot(aes(y = depthBin, x = value)) +
  geom_path() + scale_y_reverse(limits = c(1000, 0)) + scale_x_log10() +
  geom_vline(xintercept = 1) +
  geom_vline(xintercept = 0.5) +
  geom_vline(xintercept = 0.1)
oxyprof
```

```{r}
ctdP2Binned %>% filter(variable == "oxygen") %>%
  group_by(depthBin) %>% summarize(value = mean(value)) %>% filter(value < .1) %>% 
  summarize(shallow = min(depthBin), deep = max(depthBin))
```

```{r}
ctdP2Binned %>% filter(variable == "oxygen") %>%
  group_by(depthBin) %>% summarize(value = mean(value)) %>% filter(value < .5) %>% 
  summarize(shallow = min(depthBin), deep = max(depthBin))
```


# Combined profiles
,
             labeller = as_labeller(salinity = "temperature (C)")

```{r}
ctdP2Binned %>% rename(depth = depthBin) %>% filter(depth <= 1500, cast == 43) %>% ungroup() %>%
  mutate(variable = fct_relevel(variable, levels = c("temperature", "salinity", "sigmaT", "fluorescence", "oxygen", "beamAttenuation"))) %>%
  ggplot(aes(x = value, y = depth)) +
  facet_wrap(~variable, scales = "free", strip.position = "bottom") +
  scale_y_reverse() + geom_path()
```

```{r}
ctdP2Binned %>% rename(depth = depthBin) %>% filter(depth <= 1500, cast == 43) %>% ungroup() %>%
  mutate(variable = fct_relevel(variable, levels = c("temperature", "salinity", "sigmaT", "fluorescence", "oxygen", "beamAttenuation"))) %>%
  ggplot(aes(x = value, y = depth)) +
  facet_wrap(~variable, scales = "free", strip.position = "bottom",
             labeller = as_labeller(c(temperature = "Temperature (\u00B0C)", salinity = "Salinity (ppt)", sigmaT = "Density (\u03C3\u03b8)", fluorescence = "Flurescence (rfu)",
                                      oxygen = "oxygen (mg/L)", beamAttenuation = "Beam Attenuation \n (relative)"))) +
  scale_y_reverse() + geom_path() + xlab(NULL) + theme_cowplot() + theme(strip.background = element_blank(), strip.placement = "outside")

ggsave("figures/CTDSummary.svg")
```

Cryptic warning mesage that seems to come from the fct_relevel, but that doenst have an effect


# Non ggplot multiple axis

```{r}
plotData <- ctdP2Binned %>% rename(depth = depthBin) %>% filter(depth <= 1500, cast == 43) %>% ungroup() %>% select(-cast) %>%
  pivot_wider(names_from = variable, values_from = value)
plotDataCourse <- ctdP2BinnedCourse %>% rename(depth = depthBin) %>% filter(depth <= 1500, cast == 43) %>% ungroup() %>% select(-cast) %>%
  pivot_wider(names_from = variable, values_from = value)
```

Oxygen, Salinity Temperature
```{r fig.width = 4, fig.height = 5}
GlobalAdjust = -.5
#plot.new()
plotTempSalOxy <- function(){
  par(mar = c(7,4,4,1))
  plot(plotDataCourse$oxygen, plotDataCourse$depth, type = "l", ylim = c(1200, 0), col = "slateblue1", lwd = 8, ylab = "", xlab = "", xaxt = "n", yaxt = "n")
  axis(side = 3, padj = 1, tcl = .5)
  mtext( "Oxygen (µM)", side = 3, line = 1.25)
  #axis(side = 2, padj = 1, tcl = 0.5, at = seq(from = 0, to = 1200, by = 200))
  axis(side = 2, padj = .5, tcl = 0.5, las = 2, mgp = c(0, .3, 0))
   mtext("Depth (m)", side = 2, line = 2, cex = 1.25)
  #abline(h = 147, col = "darkblue") 
  abline(h = OMZBase, col = "darkblue")
  abline(h = PhoticBase, col = "darkgreen")
  #text(y = 1050, x = 175, labels = "Bottom of OMZ\n (850 m)")
  par(new = TRUE)
  plot(plotDataCourse$temperature, plotDataCourse$depth, type = "l", ylim = c(1200, 0), xlim = c(0, 30), col = "firebrick4", lwd = 2, ylab = "", xlab = "", axes = FALSE)
  axis(side = 1, line = 0, padj = GlobalAdjust, tcl = .5)
  mtext( "Temperature (°C)", side = 1, line = 2 + GlobalAdjust)
  par(new = TRUE)
  plot(plotDataCourse$salinity, plotDataCourse$depth, type = "l", ylim = c(1200, 0), col = "gray20", lty = "dashed", lwd = 3, axes = FALSE, xlab = "", ylab = "")
  axis(side = 1, line = 3.5, padj = -1, tcl = .5)
  mtext("Salinity (ppt)", side = 1, line = 5 + GlobalAdjust/2)
  legend(x = 33.95, y = 900, legend = c("Oxygen", "Temp", "Sal"), lty = c("solid", "solid", "dashed"), col = c("slateblue1", "firebrick4", "gray20"), lwd = c(8, 2, 3))
  mtext(expression(bold("B")), side = 3, line = 1.3, adj = 0, cex = 2)
}
plotTempSalOxy()
```

Oxygen, Beam, Sigma T
```{r fig.width = 4, fig.height = 5}
plotBeamSTOxy <- function(){
  par(mar = c(7,4,4,1))
  
  plot(plotDataCourse$sigmaT, plotDataCourse$depth, type = "l", ylim = c(1200, 0), col = "gray40", lty = "dotted", lwd = 5, axes = FALSE, xlab = "", ylab = "")
  #axis(side = 1, line = 2, at = 21:26)
  axis(side = 2, padj = 1, tcl = 0.5)
   mtext("Depth (m)", side = 2, line = 2, cex = 1.25)
  axis(side = 1, line = 3,  padj = GlobalAdjust, tcl = .5)
  #mtext(expression(Density~σθ~(kg/m^3)), side = 1, line = 2.2, adj = 1)
  mtext(expression(Density~σθ~(kg/m^3)), side = 1, line = 4.75)
  mtext("Depth (m)", side = 2, line = 2, cex = 1.25)
  par(new = TRUE)
  plot(plotDataCourse$oxygen, plotDataCourse$depth, type = "l", ylim = c(1200, 0), col = "slateblue1", lwd = 8, lty = "solid", ylab = "", xlab = "", axes = FALSE)
  axis(side = 3, padj = 1, tcl = .5)
  mtext( "Oxygen (µM)", side = 3, line = 1.25)
  
  par(new = TRUE)
  plot(plotDataCourse$beamAttenuation, plotDataCourse$depth, type = "l", ylim = c(1200, 0), col = "black", lwd = 3, ylab = "", xlab = "", xaxt = "n", yaxt = "n")
  #axis(side = 1, at = seq(from = 0.075, to = 0.175, by = 0.025))
  axis(side = 1, at = seq(from = 0.075, to = 0.225, by = 0.025), padj = GlobalAdjust, tcl = .5)
  #mtext( "Beam Attenuation (/m)", side = 1, line = .1, adj = 1)
  mtext( "Beam Attenuation (/m)", side = 1, line = 2 + GlobalAdjust)
  abline(h = 160, col = "darkgreen")
  abline(h = OMZBase, col = "darkblue")
  legend(x = .11, y = 900, legend = c("Oxygen", "Beam", "σθ"), lty = c("solid", "solid", "dashed"), col = c("slateblue1", "black", "gray40"), lwd = c(8, 3, 5))
  mtext(expression(bold("D")), side = 3, line = 1.3, adj = 0, cex = 2)
}
plotBeamSTOxy()

```

Oxyen, Fluo, Sigma T
```{r fig.width = 4, fig.height = 5}

plotFluSTOxy <- function(){
  par(mar = c(8,3,4,0), cex.axis = 1.3)
  plot(plotData$sigmaT, plotData$depth, type = "l", ylim = c(200, 0), col = "gray40", lty = "dotted", lwd = 5, xlab = "", ylab = "", xaxt = "n", yaxt = "n")
  axis(side = 2, padj = 1, tcl = 0.5, at = c(0, 50, 100, 150, 200))
   mtext("Depth (m)", side = 2, line = 2, cex = 1.25)
  axis(side = 1, line = 4 + GlobalAdjust, padj = GlobalAdjust, tcl = .5)
  mtext(expression(Density~σθ~(kg/m^3)), side = 1, line = 7 + GlobalAdjust * 2)
  par(new = TRUE)
  plot(plotData$oxygen, plotData$depth, type = "l", ylim = c(200, 0), col = "slateblue1", lwd = 8, ylab = "", xlab = "", axes = FALSE)
  axis(side = 3, padj = 1, tcl = .5)
  mtext("Oxygen (µM)", side = 3, line = 1.5)
  
  par(new = TRUE)
  plot(plotData$fluorescence, plotData$depth, type = "l", ylim = c(200, 0), xlim = c(0, max(plotData$fluorescence) * 1.2), col = "darkgreen", lty = "solid", lwd = 3, axes = FALSE, xlab = "", ylab = "")
  axis(side = 1, line = 0, padj = GlobalAdjust, tcl = .5)
  mtext("Fluorescence (RFU)", side = 1, line = 1.5)
  abline(h = 160, col = "darkgreen")
    abline(h = OMZTop, col = "darkblue")
  #text(labels = "Base of\nPhotic Zone\n(160 m)", x = 1.9, y = 215)
  
  legend(x = .6, y = 130, legend = c("Oxygen", "Fluo", "σθ"), lty = c("solid", "solid", "dotted"), col = c("slateblue1", "darkgreen", "gray40"), lwd = c(8, 3, 5))
  mtext(expression(bold("C")), side = 3, line = 1.3, adj = 0, cex = 2)
}
plotFluSTOxy()
```

Oxyen, Fluo, PAR

```{r}
claraPARAvg <- claraPAR %>% group_by(depth) %>% summarize(PAR = mean(PAR), PARPct = mean(PARPct))
```

```{r}
claraPARFirst <- claraPAR %>% filter(Hr == first(Hr))
```


```{r}
plot(log10(claraPARFirst$PARPct), claraPARFirst$depth, ylim = c(200, 0), xlim = c(-6, 0), type = "l")
```


```{r fig.width = 4, fig.height = 5}

plotFluPAROxy <- function(){
  par(mar = c(8,3,4,0), cex.axis = 1.3)
  plot(log10(claraPARFirst$PARPct), claraPARFirst$depth, ylim = c(200, 0), xlim = c(-6, 0), type = "l", col = "gray10", lty = "solid", lwd = 2, xlab = "", ylab = "", xaxt = "n", yaxt = "n")
  #plot(plotData$sigmaT, plotData$depth, type = "l", ylim = c(200, 0), col = "gray40", lty = "dotted", lwd = 5, xlab = "", ylab = "", xaxt = "n", yaxt = "n")
  axis(side = 2, padj = 1, tcl = 0.5, at = c(0, 50, 100, 150, 200))
  mtext("Depth (m)", side = 2, line = 2, cex = 1.25)
  axis(side = 1, line = 4 + GlobalAdjust, padj = GlobalAdjust, tcl = .5)
  mtext(expression(log[10](PAR/Surface~PAR)), side = 1, line = 7 + GlobalAdjust * 2)
  par(new = TRUE)
  plot(plotData$oxygen, plotData$depth, type = "l", ylim = c(200, 0), col = "slateblue1", lwd = 8, ylab = "", xlab = "", axes = FALSE)
  axis(side = 3, padj = 1, tcl = .5)
  mtext("Oxygen (µM)", side = 3, line = 1.5)
  
  par(new = TRUE)
  plot(plotData$fluorescence, plotData$depth, type = "l", ylim = c(200, 0), xlim = c(0, max(plotData$fluorescence) * 1.2), col = "darkgreen", lty = "solid", lwd = 3, axes = FALSE, xlab = "", ylab = "")
  axis(side = 1, line = 0, padj = GlobalAdjust, tcl = .5)
  mtext("Fluorescence (RFU)", side = 1, line = 1.5)
  abline(h = 160, col = "darkgreen")
  abline(h = OMZTop, col = "darkblue")
  #text(labels = "Base of\nPhotic Zone\n(160 m)", x = 1.9, y = 215)
  
  legend(x = .6, y = 130, legend = c("Oxygen", "Fluo", "PAR"), lty = c("solid", "solid", "solid"), col = c("slateblue1", "darkgreen", "gray20"), lwd = c(8, 3, 2))
  mtext(expression(bold("C")), side = 3, line = 1.3, adj = 0, cex = 2)
}
plotFluPAROxy()
```

Map
```{r}
library(imager)
ETNPmap <- load.image("figures/ETNP.png")
plotMap <- function(){
  par(mar = c(0,2,2,0))
  plot(ETNPmap, axes = FALSE)
  mtext(expression(bold("A")), side = 3, line = 0, adj = 0, cex = 2)
}
plotMap()
```






```{r, fig.width = 10, fig.height = 8}
StationInfoPlot <- function(){
# layout(matrix(c(1, 1, 1, 1, 1, 1, 2, 2, 2, 2,
#                 1, 1, 1, 1, 1, 1, 2, 2, 2, 2,
#                 3, 3, 3, 3, 3, 4, 4, 4, 4, 4, 
#                 3, 3, 3, 3, 3, 4, 4, 4, 4, 4, 
#                 3, 3, 3, 3, 3, 4, 4, 4, 4, 4
# )
# ,5, 10, byrow = TRUE))
  
  layout(matrix(c(1, 1, 1, 1, 1, 1, 2, 2, 2, 2,
                1, 1, 1, 1, 1, 1, 2, 2, 2, 2,
                #3, 3, 3, 3, 3, 4, 4, 4, 4, 4, 
                3, 3, 3, 3, 3, 4, 4, 4, 4, 4, 
                3, 3, 3, 3, 3, 4, 4, 4, 4, 4
)
,4, 10, byrow = TRUE))
plotMap()
plotFluPAROxy()
plotTempSalOxy()
plotBeamSTOxy()
}
StationInfoPlot()
```


I'm bored, and going to futz with this more later.

# Another attempt
Same figure A. 
B is as before
C we remove density
D we remove oxygen, density to axis 2

Oxyen, Fluo
```{r fig.width = 4, fig.height = 5}

plotFluOxy <- function(){
  par(mar = c(4,3,4,0), cex.axis = 1.3)

  plot(plotData$oxygen, plotData$depth, type = "l", xlim = c(0, 210), ylim = c(200, 0), col = "slateblue1", lwd = 8, ylab = "", xlab = "", axes = FALSE)
  #axis(side = 2, padj = 1, tcl = 0.5, at = c(0, 50, 100, 150, 200))
  axis(side = 2, padj = .5, tcl = 0.5, las = 2, mgp = c(0, .3, 0), at = c(0, 50, 100, 150, 200))
   mtext("Depth (m)", side = 2, line = 2, cex = 1.25)
  axis(side = 3, padj = 1, tcl = .5, at = c(0, 50, 100, 150, 200))
  mtext("Oxygen (µM)", side = 3, line = 1.5)
  
  par(new = TRUE)
  plot(plotData$fluorescence, plotData$depth, type = "l", ylim = c(200, 0), xlim = c(0, max(plotData$fluorescence) * 1.2), col = "darkgreen", lty = "solid", lwd = 3, axes = FALSE, xlab = "", ylab = "")
  axis(side = 1, line = 0, padj = GlobalAdjust, tcl = .5)
  mtext("Fluorescence (RFU)", side = 1, line = 1.5)
  abline(h = 160, col = "darkgreen")
  #text(labels = "Base of\nPhotic Zone\n(160 m)", x = 1.9, y = 215)
  
  legend(x = .6, y = 130, legend = c("Oxygen", "Fluo"), lty = c("solid", "solid"), col = c("slateblue1", "darkgreen"), lwd = c(8, 3))
  mtext(expression(bold("C")), side = 3, line = 1.3, adj = 0, cex = 2)
}
plotFluOxy()
```

Beam, Sigma T
```{r fig.width = 4, fig.height = 5}
plotBeamST <- function(){
  par(mar = c(7,4,4,1))
  
  plot(plotDataCourse$sigmaT, plotDataCourse$depth, type = "l", ylim = c(1200, 0), col = "gray40", lty = "dotted", lwd = 5, axes = FALSE, xlab = "", ylab = "")
  #axis(side = 1, line = 2, at = 21:26)
  axis(side = 2, padj = .5, tcl = 0.5, las = 2, mgp = c(0, .3, 0))
   mtext("Depth (m)", side = 2, line = 2, cex = 1.25)
  axis(side = 3, line = 0,  padj = 1, tcl = .5)
  #mtext(expression(Density~σθ~(kg/m^3)), side = 1, line = 2.2, adj = 1)
  mtext(expression(Density~σθ~(kg/m^3)), side = 3, line = 1)
  
  
  par(new = TRUE)
  plot(plotDataCourse$beamAttenuation, plotDataCourse$depth, type = "l", ylim = c(1200, 0), col = "black", lwd = 3, ylab = "", xlab = "", xaxt = "n", yaxt = "n")
  #axis(side = 1, at = seq(from = 0.075, to = 0.175, by = 0.025))
  axis(side = 1, at = seq(from = 0.075, to = 0.225, by = 0.025), padj = -1, tcl = .5)
  #mtext( "Beam Attenuation (/m)", side = 1, line = .1, adj = 1)
  mtext( "Beam Attenuation (/m)", side = 1, line = 2 + GlobalAdjust)
  abline(h = 160, col = "darkgreen")
  abline(h = OMZBase, col = "darkblue")
  legend(x = .11, y = 900, legend = c("Beam", "σθ"), lty = c("solid", "dashed"), col = c( "black", "gray40"), lwd = c(8, 3, 5))
  mtext(expression(bold("D")), side = 3, line = 1.3, adj = 0, cex = 2)
}
plotBeamST()

```


```{r, fig.width = 10, fig.height = 8}
StationInfoPlot <- function(){
layout(matrix(c(1, 1, 1, 1, 1, 1, 2, 2, 2, 2,
                1, 1, 1, 1, 1, 1, 2, 2, 2, 2,
                #3, 3, 3, 3, 3, 4, 4, 4, 4, 4, 
                3, 3, 3, 3, 3, 4, 4, 4, 4, 4, 
                3, 3, 3, 3, 3, 4, 4, 4, 4, 4
)
,4, 10, byrow = TRUE))
plotMap()
plotFluPAROxy()
plotTempSalOxy()
plotBeamST()
}
StationInfoPlot()
```

```{r}
png(filename = "./figures/CombinedP2Info.png", width = 10, height = 8, units = "in", res = 200)
StationInfoPlot()
dev.off()
```