---
title: "R Notebook"
output: html_notebook
---

First I want a highly interpolated smoothed data set.
Same size bins as usual, but depths by meter, or 1/10 meter. I want the change in flux to be like < 1%.

Then I get adjusted DF for every depth.
Then I run remin_shuffle on each depth and extract Cr.


Start with bes. I am assuming I have the usual data. I also have SameGam from GenerateFigures.Rmd, which I think is ready to go.
```{r}
fine_depths <- seq(from = 1, to = 1500, by = 5)

lbbs_FD <- tibble(lb = lb_vec, binsize = binsize_vec)
Expanded_FD <- expand_grid(time = as.factor(unique(besE$time)), lb = lb_vec, depth = BianchiBins[2:length(BianchiBins)]) %>%
  left_join(lbbs_FD, by = "lb")

pt0 <- proc.time()
Pred_FD <- exp(predict(SameGam, Expanded_FD))
pt1 <- proc.time()
pt1 - pt0
Thing_FD <- bind_cols(Expanded_FD, nnparticles = Pred_FD) %>% mutate(time = as.character(time)) %>% mutate(nparticles = nnparticles * binsize)
```
Too slow
Hey. Here's an idea. Instead of slicing everything super thin, I could just calculate at the BES locations and like 1m below those locations.
And then I look at jumps between each depth and the depth below

```{r}
space <- 0.01
Expanded_FD_Above <- Expanded_FD %>%
  mutate(depth = depth - space)
Pred_FD_Above <- exp(predict(SameGam, Expanded_FD_Above))
Thing_FD_Above <- bind_cols(Expanded_FD_Above, nnparticles = Pred_FD_Above) %>% mutate(time = as.character(time)) %>% mutate(nparticles = nnparticles * binsize)
```

```{r}
Thing_FD_2 <- bind_cols(Thing_FD, depth_above = Thing_FD_Above$depth, nnparticles_above = Thing_FD_Above$nnparticles, nparticles_above = Thing_FD_Above$nparticles) %>%
  mutate(flux = nparticles * C_f_global * lb ^ ag_global,
         flux_above = nparticles_above * C_f_global * lb ^ ag_global)
```

```{r}
Thing_FD_Nested <- Thing_FD_2 %>% group_by(time, depth) %>% 
  nest() %>%
  mutate(spec_only = map(data, ~pull(., nparticles)),
         spec_prev = map(data, ~pull(., nparticles_above))
  )
```


           DF = smooth_flux_fit - flux_prev,
           #DFP = 1 - DF/flux_prev,  # I was using this for a while.
           DFP = smooth_flux_fit/flux_prev,
           depth_prev = lag(depth),
           DZ = depth - depth_prev,

```{r}
Thing_FD_FSum <- Thing_FD_2 %>% group_by(time, depth, depth_above) %>% 
  summarize(Flux = sum(flux), Flux_Above = sum(flux_above)) %>%
  mutate(DF = Flux - Flux_Above,
         DFP = Flux/Flux_Above,
         DZ = depth - depth_above)

Thing_FD_FSum
```

```{r}
Thing_FD_3 <- left_join(Thing_FD_FSum, Thing_FD_Nested, by = c("time", "depth"))
Thing_FD_3
```

```{r}
Thing_FD_4 <- Thing_FD_3 %>%
  mutate(use_DFP = map2_dbl(spec_prev, DFP, optFun, llb = little_lb))
Thing_FD_4
```

```{r}
Thing_FD_4 %>% ungroup() %>% summarize(DFPMin = min(DFP), UseDFPMin = min(use_DFP))
```

I've been misspecifying alpha and gamma in the remin model.
```{r}
#loc_rs <- function(abun_in, DFpct, DeltaZ){remin_shuffle()}
Thing_FD_5 <- Thing_FD_4 %>%
  mutate(Remin = pmap(list(spec_prev, use_DFP, DZ), remin_shuffle)) %>%
  mutate(Cr = map_dbl(Remin, ~.$Cr))
Thing_FD_5
```

```{r}
ggplot(Thing_FD_5, aes(y = depth, x = pracma::nthroot(Cr, 5), color = as.factor(time))) + geom_point() + scale_y_reverse(limits = c(1500, 0))
```

```{r}
ggplot(Thing_FD_5, aes(y = depth, x = pracma::nthroot(DFP, 5), color = as.factor(time))) + geom_point() + scale_y_reverse(limits = c(1500, 0))
```
