---
title: "R Notebook"
output: html_notebook
---

Generates figures of EK60 Data

Load in libraries

```{r}
library(tidyverse)
library(lubridate)
```

```{r}
PhoticBase <- 160
OMZBase <- 900
DVMBase <- 600
OMZTop <- 90
```

## EK60

Read in the data,
I processed these data elsewhere, so as to avoid overloading this directory with intermediate files.
03 October 2021 -- Specify that times are in UTC (not local time relative to the person using the code)
```{r}
dataBinned <- read_csv("data/backscatter_table_go7.csv") #, locale = locale(encoding = "latin1", tz="UTC"))
```


Convet to local time zone
```{r}
dataBinned_01 <- dataBinned %>%
  mutate(timeMex = with_tz(time_bin, tzone = "Mexico/General"))
```

Some upfront calculations
```{r}
startDay <- dataBinned_01$timeMex %>% na.omit %>% min %>% floor_date(unit = "days")
endDay <- dataBinned_01$timeMex %>% na.omit %>% max %>% ceiling_date(unit = "days")
timeBreaks <- seq(from = startDay, to = endDay, by = "12 hours")
timeLabels <- format(timeBreaks)
```

```{r}
library(suncalc)
SunTime <- getSunlightPosition(date = unique(dataBinned_01$timeMex), lat = 16.6, lon = -106.9, keep = "altitude") %>%
  filter(!is.na(date)) %>%
  rename(timeMex = date) %>%
  arrange(timeMex)
```

```{r}
SunTime %>% ggplot(aes(x = timeMex, col = altitude > 0)) + geom_line(aes(y = altitude), size = 2)
```



Adding cast times

```{r}
bes<- read_csv("dataOut/binned_EachSize.csv")
castTimes <- bes %>% filter(project == "ETNP") %>% group_by(time) %>% summarise(depth = max(depth)) %>% mutate(depth = if_else(depth > 1000, 1000, depth))
castTimes
```





Plot the 18kHz data (largish animals)
```{r}

# Position of letters
plotLetters <- tribble(
  ~letter, ~depth_bin, ~timeMex,
  "A", 350, as.POSIXct("2017-01-07 13:00:00"),
  "B", 200, as.POSIXct("2017-01-09 23:00:00"),
  "C", 150, as.POSIXct("2017-01-08 13:00:00"),
  "D", 625, as.POSIXct("2017-01-12 07:00:00"),
  "E", 750, as.POSIXct("2017-01-10 02:00:00")
  
)

library(shadowtext)
plot18k <- dataBinned_01 %>% filter(frequency == 18000) %>% ggplot(aes(x = timeMex, y = depth_bin, fill = value)) + geom_tile() + scale_y_reverse() + scale_fill_viridis_c(limits = c(-165, -75), oob = scales::squish) +
  scale_x_datetime(breaks = timeBreaks, date_labels = "%d::%H") + labs(x = "Day::Hour", y = "Depth (m)", fill = "Backscatter (dB)") + theme_bw() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) + geom_hline(yintercept = PhoticBase, color = "darkgreen") +
  geom_hline(yintercept = OMZBase, color = "darkblue") +
    geom_hline(yintercept = OMZTop, color = "darkblue") +
  #geom_hline(yintercept = 600, color = "darkgoldenrod", lty = "dashed") +
  geom_shadowtext(data = plotLetters, aes(x = timeMex - 12 * 60^2, y = depth_bin, label = letter),  inherit.aes = FALSE, size = 6, bg.color = "white", color = "black") +
  geom_segment(data = plotLetters, inherit.aes = FALSE, aes(x = timeMex - 9 * 60^2, xend = timeMex, y = depth_bin, yend = depth_bin), arrow = arrow(length = unit(0.03, "npc")), color = "white", size = 1.5) + 
  geom_segment(data = plotLetters, inherit.aes = FALSE, aes(x = timeMex - 9 * 60^2, xend = timeMex, y = depth_bin, yend = depth_bin), arrow = arrow(length = unit(0.03, "npc"))) +
  # sunlight times
  geom_point(aes(x = timeMex + 60^2, col = altitude > 0), y = -1, size = 2, data = SunTime, inherit.aes = FALSE, shape = 15) + scale_color_manual(values = c("black", "yellow")) +
  # cast times
  geom_point(data = castTimes, aes(x = time, y = depth),  inherit.aes = FALSE, shape = 23, color = "white", fill = "black", size = 4) # confirm timezones
plot18k

ggsave("figures/stationP2_EK60_18kOnly.png")
```

I added the day night bar to the top, but it still looks a little off center. I recall the zooplankton surfacing exactly when solar angle was zero.
I've temporarily added one hour, which centers things (indicating I'm somehow off by one hour with the solar angle function), but also the days are too short, relative to the zooplantkon.




To do, add cast times.

Plot all of the other sizes of things

```{r fig.height=20, fig.width = 8}
dataBinned_01 %>% ggplot(aes(x = timeMex, y = depth_bin, fill = value)) + geom_tile() + scale_y_reverse() + scale_fill_viridis_c(limits = c(-165, -75), oob = scales::squish) +
  scale_x_datetime(breaks = timeBreaks, date_labels = "%d::%H") + labs(x = "Day::Hour", y = "Depth (m)", fill = "Backscatter (dB)") + theme_bw() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  geom_hline(yintercept = PhoticBase, color = "darkgreen") +
  geom_hline(yintercept = OMZBase, color = "darkblue") +
    geom_hline(yintercept = OMZTop, color = "darkblue") +
  
  
  facet_wrap(~frequency, ncol = 1)

#ggsave("figures/stationP2_EK60_go7.svg", width = 4, height = 10)
ggsave("figures/stationP2_EK60_go7.png", width = 6, height = 10)
```