---
title: "R Notebook"
output: html_notebook
---

Goal here is to compare observed and normalized flux from the UVP.

# Load libraries

```{r}
library(tidyverse)
library(readxl)
library(cowplot)
```


# Bring in all data.
## UVP
```{r}
unbinned_DepthSummary <- read_csv("dataOut/unbinned_DepthSummary.csv")
unbinned_EachSize <- read_csv("dataOut/unbinned_EachSize.csv")
binned_DepthSummary <- read_csv("dataOut/binned_DepthSummary.csv")
binned_EachSize <- read_csv("dataOut/binned_EachSize.csv")
```

## Flux
```{r}
fluxMS_distilled <- read_csv("dataOut/fluxMS_distilled")
```

# Redo Proctrap's power law

# Power law flux model
```{r}
loglogCfluxmod <- glm(log10(C_flux_umol) ~ log10(Depth), data = fluxMS_distilled)
summary(loglogCfluxmod)
```


# Interpolate predicted flux profile
In non log space, added out of order on 06 December 2018

```{r}
CPred <- tibble(
  Depth = c(seq(from = 30, to = 150, by = 0.1),
            seq(from = 101, to = 1000, by = 1)
  )
) 
CPred$C_flux_umol <- 10^predict(loglogCfluxmod, CPred)
```

## Flux profile for poster
```{r}
FDP1 <- fluxMS_distilled %>% ggplot(aes(y = Depth, x = C_flux_umol)) +
    geom_point(data = CPred, aes(y = Depth, x = C_flux_umol), size = 0.1, colour = "gray30") +
  geom_point(aes(color = SampleType, shape = TrapType), size = 5) +
  scale_y_continuous(trans = "reverse") +
  scale_x_continuous(limits = c(0, 200)) + 
  theme_bw() 

FDP1
#ggsave("figures/CFlux.svg", width = 7, height = 7)
```

# Estimated flux

```{r}
plot_flux <- binned_DepthSummary %>% ggplot(aes(x = tot_flux, y = depth, colour = profile)) + geom_point(alpha = 0.5, size = 1) + scale_y_reverse(limits = c(1000,0)) + scale_x_log10() + guides(colour = FALSE) + labs(x = "Unadjusted Flux (units/m^2/day)")+
   theme_cowplot()
plot_flux
```

```{r}
pre_flux_compare <- binned_DepthSummary %>% group_by(depth) %>% summarize(tot_flux = mean(tot_flux)) %>%
  mutate(Depth = depth) %>% mutate(CFlux_trap_est = 10^predict(loglogCfluxmod, .))
```

```{r}
pre_flux_compare %>% filter(Depth < 500) %>% ggplot(aes(x = tot_flux, y = CFlux_trap_est,  color = Depth)) + geom_point()  + scale_color_viridis_c(direction = -1) + scale_x_continuous() + scale_y_continuous()
```

```{r}
pre_flux_compare %>% filter(Depth < 1000) %>% ggplot(aes(x = tot_flux, y = CFlux_trap_est,  color = Depth)) + geom_point()  + scale_color_viridis_c(direction = -1) + scale_x_log10() + scale_y_continuous()
```

These do not appear to be linearly related, at least for shallow depths. Total flux overestimates relative to trap flux.

Which do I believe more?

Lets say the trap flux. In that case, we could do a fit where total uvp flux is normalized to trap estimates, even in a non linear fashion.

So I'd do a regression where CFlux_trap ~ log10(tot_flux), and then I'd plot the predicted CFlux trap from the actual total flux. Thats my new power law.

```{r}
mod1 <- lm(CFlux_trap_est ~ log10(tot_flux), data = pre_flux_compare)
summary(mod1)
plot(mod1)
```

```{r}
#rmse(mod1)
```


```{r}
flux_compare <- pre_flux_compare %>% mutate(tn_flux = predict(mod1, .))
```

```{r}
flux_compare %>% ggplot(aes(y = Depth, x = tn_flux))  + scale_y_reverse() + geom_point(aes(x = Depth, y = CFlux_trap_est), shape = 2, size = 2)
```

```{r}
flux_compare %>% ggplot(aes(y = Depth, x = CFlux_trap_est))  + scale_y_reverse() + geom_point()
```

```{r}
binned_DepthSummary_01 <- binned_DepthSummary %>% mutate(tn_flux = predict(mod1, .))
```


FDP1 <- fluxMS_distilled %>% ggplot(aes(y = Depth, x = C_flux_umol)) +
    geom_point(data = CPred, aes(y = Depth, x = C_flux_umol), size = 0.1, colour = "gray30") +
  geom_point(aes(color = SampleType, shape = TrapType), size = 5) +

```{r}
plot_flux <- binned_DepthSummary_01 %>% rename(Depth = depth) %>% ggplot(aes(x = tn_flux, y = Depth)) + geom_point(alpha = 0.5, size = 1, aes(color = profile)) + scale_y_reverse(limits = c(1000,0)) + scale_x_log10()  + labs(x = "Adjusted Flux (microMoles/m^2/day)")+
   theme_cowplot() + geom_point(aes(y = Depth, x = C_flux_umol, fill = SampleType, shape = TrapType), colour = "black", stroke = 1, size = 5, data = fluxMS_distilled) +
  scale_shape_manual(values = c(25, 22))+
  scale_size_manual(values = c(3, 4)) 
plot_flux
```
This looks about an order of magnitude lowe rthan VanMooy 2002 or Harnett in that. Is it actually super low flux, or have I screwed up the math somewhere?
Talk with Clara, and then Jacqui and Meg.

Also, I'm having trouble with border color on the shapes. they are red. Fails if I don't specify a color.

```{r}
ggplot() + geom_point(aes(y = Depth, x = C_flux_umol), data = fluxMS_distilled)
```

I think that maybe the alpha + gamma term is wrong, and thats why we have a non linear fit. We could try to minimize the R^2 value of the fit, while choosing 
C_f and alpha + gamma

```{r}
C_f_test <- 1
ag_test <- 1.7 + 1.7 - 1

fit_flux_es <- function( C_f, ag, ES1 = binned_EachSize){
ES2 <- binned_EachSize %>% mutate(flux2 = C_f * nparticles * lb ^ ag)
ES2
}

#ES2 <- fit_flux_es(C_f_test, ag_test) %>% select(profile:depth, flux, flux2) # flux == flux2

 fit_flux_ds <- function(C_f, ag, ES2, DS1 = binned_DepthSummary_01){
  DS2 <- ES2 %>%
    group_by(profile, time, depth) %>%
    summarize(tot_flux2 = sum(flux2))
  
  DS2 <- left_join(DS1, DS2, by = c("profile", "time", "depth"))
}

#DS2 <- fit_flux_ds(C_f_test, ag_test, ES2)

#DS2 %>% select(profile:depth, tot_flux, tot_flux2) # flux == flux2

fit_flux <- function(C_f, ag, ES1, DS1){
  ES2 <- fit_flux_es(C_f, ag, ES1)
  DS2 <- fit_flux_ds(C_f, ag, ES2, DS1)
  return(list(ES = ES2, DS = DS2))
}

FFTest <- fit_flux(C_f_test, ag_test, binned_EachSize, binned_DepthSummary_01)

# https://stackoverflow.com/questions/43123462/how-to-obtain-rmse-out-of-lm-result
RMSE <- function(mod){
  RSS <- c(crossprod(mod$residuals))
  MSE = RSS/ length(mod$residuals)
  RMSE = sqrt(MSE)
}

# Close, but too much weight on larger values
flux_check <- function(DS){
  #diff = log10(DS$tn_flux) - log10(DS$tot_flux2)
  diff = log(DS$tn_flux) - log(DS$tot_flux2)
  squares = diff ^2
  rss = sum(squares)
  mse = rss/length(rss)
  rmse = sqrt(mse)
  rmse
}

#flux_check(FFTest$DS)

fit_check_flux <- function(C_f, ag, ES1, DS1){
  FF <- fit_flux(C_f, ag, ES1, DS1)
  FC <- flux_check(FF$DS)
  FC
}

fit_check_flux(C_f_test, ag_test, binned_EachSize, binned_DepthSummary_01)

fc_wrap <- function(x){
  C_f <- x[1]
  ag <- x[2]
  FC <- fit_check_flux(C_f, ag, binned_EachSize, binned_DepthSummary_01)
  FC
}
```
I'm getting two f values for my tests. 248 and 306. Not sure what gives, but not going to dig right now. 02 Feb 2019

Now iterate over all reasonable C_f and ag

```{r}
opt <- optim(c(C_f_test, ag_test), fc_wrap)
opt
```



```{r}
fit_alpha = (opt$par[2] +1)/2
fit_alpha
fit_gamma = fit_alpha - 1
fit_gamma
```

So in this scenario, big particles sink slower than small particles.

```{r}
#opt <- optim(c(C_f_test, ag_test), fc_wrap, method = "L-BFGS-B", lower = c(0, 0), upper = c(Inf, 10))
#opt
```

I don't get it. Why is ag so frigging high?
Why does Cf try to zero out. Next step is to look at what happens if I use these values and investigate the output.
Also the value parameters look bad, in general.

```{r}
OptFlux <- fit_flux(opt$par[1], opt$par[2], binned_EachSize, binned_DepthSummary_01)
binned_EachSize_02 <- OptFlux$ES
binned_DepthSummary_02 <- OptFlux$DS
```

This isn't working. Things don't actually fit well with this optimum fit.

```{r}
flux_check(binned_DepthSummary_02)
```

Changing the C_f parameter isn't improving the vit

Debugging

```{r}
mod2 <- lm(tn_flux~tot_flux2, data = binned_DepthSummary_02)
summary(mod2)
```
Oh. I don't want to do LM. It always rescales so C_f doesn't have any effect.
I want to calculate RMSE by hand.
EG. Get difference between each trap and predicted flux, square them, add them, devide by length, take the square root, or even just square and add.

# Plot check

```{r}
binned_DepthSummary_02 %>% group_by(depth) %>% summarize(tot_flux2 = mean(tot_flux2)) %>% ggplot(aes(y = depth))  + scale_y_reverse(limits = c(1000, 0)) + scale_x_continuous(limits = c(0, 200)) +
  geom_point(aes(y = Depth, x = C_flux_umol, fill = SampleType, shape = TrapType), colour = "black", stroke = 1, size = 5, data = fluxMS_distilled) +
  geom_point(aes(x = tot_flux2)) +
scale_shape_manual(values = c(25, 22))+
  scale_size_manual(values = c(3, 4)) +
  ylab("Depth (m)") + xlab("Flux micro-mol/m^2/day")
  
```

```{r}
binned_DepthSummary_02 %>% group_by(depth) %>% summarize(tot_flux2 = mean(tot_flux2)) %>% ggplot(aes(y = depth))  + scale_y_reverse(limits = c(2500, 0)) + scale_x_continuous(limits = c(0, 110)) +
  geom_point(aes(y = Depth, x = C_flux_umol, fill = SampleType, shape = TrapType), colour = "black", stroke = 1, size = 5, data = fluxMS_distilled) +
  geom_point(aes(x = tot_flux2)) +
scale_shape_manual(values = c(25, 22))+
  scale_size_manual(values = c(3, 4)) +
  ylab("Depth (m)") + xlab("Flux micro-mol/m^2/day")
  
```

binned_DepthSummary_02

```{r}
write_csv(binned_DepthSummary_02, "dataOut/binned_DepthSummary_02.csv")
```

# 02 April 2019
# Fitting directly to traps
Alternative approach. What if, instead of fitting a power law to flux and "up sampling" I instead down sample the UVP data to match the flux. I could do this, for instance by coursely binning and then just taking the nearist bin.

```{r}
trapDepths <- fluxMS_distilled  %>% pull(Depth) %>% unique
trapDepths

uvpDepths <- binned_EachSize %>% filter(profile == "stn_043") %>% pull(depth) %>% unique
uvpDepths
```

```{r}
nearist <- function(dep, dvec = uvpDepths){dvec[which.min(abs(dvec - dep))]}
nearist(69)

```

```{r}
fluxMS_distilled %>% mutate(NearistUVPDepth = map_dbl(Depth, nearist))
```

```{r}
left_join(
  fluxMS_distilled %>% mutate(NearistUVPDepth = map_dbl(Depth, nearist)),
  binned_DepthSummary_02 %>% filter(profile == "stn_043") %>% select(depth, tot_flux2),
  by = c("NearistUVPDepth" = "depth")
)
```

BOOKMARK 02 April 2020
```{r}

fluxMS_distilled_connect <- fluxMS_distilled %>% mutate(NearistUVPDepth = map_dbl(Depth, nearist))

flux_check_vs_traps <- function(DS, FLX = fluxMS_distilled_connect){
  
  thing <- left_join(
    FLX,
    DS %>% filter(profile == "stn_043") %>% select(depth, tot_flux2),
    by = c("NearistUVPDepth" = "depth")
                     )
  
  #diff = log10(DS$tn_flux) - log10(DS$tot_flux2)
  diff = log(thing$C_flux_umol) - log(thing$tot_flux2)
  squares = diff ^2
  rss = sum(squares)
  mse = rss/length(rss)
  rmse = sqrt(mse)
  rmse
}

flux_check_vs_traps(binned_DepthSummary_02, fluxMS_distilled_connect)
```

Note: I'd prefer to feature rebinning.
Now I need to (1) 
```{r}
fit_check_flux_vstraps <- function(C_f, ag, ES1, DS1, FLX = fluxMS_distilled_connect){
  FF <- fit_flux(C_f, ag, ES1, DS1)
  FC <- flux_check_vs_traps(FF$DS, FLX)
  FC
}

fit_check_flux_vstraps(C_f_test, ag_test, binned_EachSize, binned_DepthSummary, fluxMS_distilled_connect)

fc_wrap_vstraps <- function(x){
  C_f <- x[1]
  ag <- x[2]
  FC <- fit_check_flux_vstraps(C_f, ag, binned_EachSize, binned_DepthSummary)
  FC
}

opt_vstraps <- optim(c(C_f_test, ag_test), fc_wrap_vstraps)
opt_vstraps
```

Seriously. Now its negative?

Post mortem

```{r}
negAlpha <- fit_flux(opt_vstraps$par[1], opt_vstraps$par[2], binned_EachSize, binned_DepthSummary)
```

```{r}
negAlpha_ES <- negAlpha$ES
negAlpha_DS <- negAlpha$DS
```

```{r}
negAlpha_DS %>% group_by(depth) %>% summarize(tot_flux2 = mean(tot_flux2)) %>% ggplot(aes(y = depth))  + scale_y_reverse(limits = c(2500, 0)) + scale_x_log10(limits = c(1, 110)) +
  geom_point(aes(y = Depth, x = C_flux_umol, fill = SampleType, shape = TrapType), colour = "black", stroke = 1, size = 5, data = fluxMS_distilled) +
  geom_point(aes(x = tot_flux2)) +
scale_shape_manual(values = c(25, 22))+
  scale_size_manual(values = c(3, 4)) +
  ylab("Depth (m)") + xlab("Flux micro-mol/m^2/day")
```

# If we don't optimize ag
Use values from Alldredge and Gotschalk
gamma = 0.26
alpha = 0.52
```{r}
alldredge_alpha = 0.52 # alldredge
alldredge_gamma = 0.26 # alldrege and gotschalk
alldredge_ag = alldredge_alpha + alldredge_gamma # Alldredge
fc_wrap_CfOnly <- function(x){
  C_f <- x[1]
  FC <- fit_check_flux(C_f, alldredge_ag, binned_EachSize, binned_DepthSummary_01)
  FC
}

opt_alldredge <- optim(c(C_f_test), fc_wrap_CfOnly, method = "Brent", lower = 0, upper = 1000)

opt_alldredge$par[2] <- alldredge_ag
opt_alldredge
```

Now that I'm running this. Alpha + gamma looks a lot more reasonalbe as 0.26. I mean, here its only 0.78.

More optomistic post mortem

```{r}
OptFlux_ald <- fit_flux(opt$par[1], opt$par[2], binned_EachSize, binned_DepthSummary_01)
binned_EachSize_ald <- OptFlux_ald$ES
binned_DepthSummary_ald <- OptFlux_ald$DS
```

```{r}
binned_DepthSummary_ald %>% group_by(depth) %>% summarize(tot_flux2 = mean(tot_flux2)) %>% ggplot(aes(y = depth))  + scale_y_reverse(limits = c(1000, 0)) + scale_x_continuous(limits = c(0, 200)) +
  geom_point(aes(y = Depth, x = C_flux_umol, fill = SampleType, shape = TrapType), colour = "black", stroke = 1, size = 5, data = fluxMS_distilled) +
  geom_point(aes(x = tot_flux2)) +
scale_shape_manual(values = c(25, 22))+
  scale_size_manual(values = c(3, 4)) +
  ylab("Depth (m)") + xlab("Flux micro-mol/m^2/day")
  
```

I'm feeling ok with this. Lets feed the aldredge optimized data into the remin model with aldredge params.

```{r}
write_csv(binned_DepthSummary_ald, "dataOut/binned_DepthSummary_ald.csv")
write_csv(binned_EachSize_ald, "dataOut/binned_EachSize_ald.csv")
```

