---
title: "R Notebook"
output: html_notebook
---

From Evans et al. 2020. Appendex 2
Data about watermasses

R.matlab allows us to port in Natalia Evan's data from her latest manuscript.
```{r}
library(tidyverse)
library(R.matlab)
```

Easy colors for a colorblind person to tell apart
```{r}
wmCols <- c("gray80", "darkorange", "darkgreen", "yellow", "white", "darkblue", "black")
```

Data from natalya evans 02 April 2020
```{r}
evansA2_00 <- readMat("data/SKQ_26_27.mat")
```

Pull data out of the matlab meta-object and turn into a tibble with the data I nead
```{r}
WaterMasses = t(evansA2_00$A)
colnames(WaterMasses) = c("13CW", "NEPIW", "AAIW")
WaterMasses <- as_tibble(WaterMasses)
Pressure <- t(evansA2_00$press)
colnames(Pressure) <- "press"
Pressure <- as_tibble(Pressure)

# convert one element matlab object to a one column tibble
mat_to_tib <- function(mob, mobname = "thing"){
  Thing = t(mob)
  colnames(Thing) = mobname
  Thing = as_tibble(Thing)
}

Lat = mat_to_tib(evansA2_00$lat, "lat")
Lon = mat_to_tib(evansA2_00$lon, "long")

WaterMasses = bind_cols(Lat, Lon, Pressure, WaterMasses)
```

Where were the data collected?
```{r}
evans_LL <- WaterMasses %>%
  select(long, lat) %>% distinct()
evans_LL %>%
  ggplot(aes(x = long, y = lat)) + geom_point()
```

Plot the locations of the samples on a map
```{r}
library("rnaturalearth")
library("rnaturalearthdata")
library("sf")
```

```{r}
oceanData <- ne_download(scale = 10, type = "coastline", category = "physical", returnclass = "sf")
```

```{r}
mexMap <- ggplot(data = oceanData) +
  geom_sf(color = "black", fill = "grey90") +
  coord_sf(xlim = c(-120, -100), ylim = c(13.5, 18)) +
  geom_point(data = evans_LL, aes(x = long, y = lat))
mexMap
```

Unless specified otherwise, measurements were taken on board the R/V Sikuliaq from 07 January 2017 through 13 January 2017 at 16.5°N 106.9°W

```{r}
evans_Target <- WaterMasses %>%
  filter(long > -107.1, long < -106.8, lat < 16.6, lat > 16.4)
```

```{r}
wmNames = c("13CW", "NEPIW", "AAIW")
evans_Target_01 <- evans_Target %>% 
  #filter(pdens < 27) %>%
  select(press, `13CW`, NEPIW, AAIW) %>% 
  pivot_longer(cols = -press, names_to = "watermass") %>%
  mutate(watermass = factor(watermass, levels = wmNames, ordered = TRUE))
```

Plot the data
```{r}
evans107Plot <- evans_Target_01 %>%
  arrange(press) %>%
  #filter(watermass != "UCDW") %>%
  #filter(value > 0) %>%
  mutate(value = if_else(value > 1, 1, value)) %>%
  ggplot(aes(x = value, y = press, fill = watermass, shape = watermass, group = watermass)) +
  geom_point(size = 3) +
  #geom_path(color = "black") +
  scale_y_reverse(limits = c(500, 100), breaks = seq(from = 0, to = 1000, by = 100)) +
  #scale_y_reverse() +
  scale_x_continuous(limits = c(0, 1)) +
  scale_fill_manual(values = c(`13CW` = "Yellow", NEPIW = "Blue", AAIW = "Black")) + scale_shape_manual(values = c(21:25, 21:25)) +
  geom_hline(yintercept = 160, color = "darkgreen") +
  theme_bw()
evans107Plot
```

Save the plot
```{r}
ggsave("figures/evans16p5N107W.png", evans107Plot, width = 5, height = 3, dpi = 100)
```

