---
title: "R Notebook"
output: html_notebook
---
Question: How does the transport by zooplankton effect transfer efficiency.
For instance, what if we identified the slope of a martin curve, from below 500m (where the flux attenuation follows a nice power law), took the flux at 175m (base of photic) and estemated the flux at 1000m.
Then get the actual flux at 1000m.

Flux_1000m - Flux_1000m Estimated / Flux 1000m Estimated = % change in flux due to zooplankton transport

```{r}
disphotic <- DS01  %>% filter(profile %in% c("stn_032", "stn_043"), depth >= 175)
fplt <- disphotic %>%
  ggplot(aes(x = depth, y = tot_flux_fit, col = profile)) + geom_point() + scale_x_log10(limits = c(175, NA)) + scale_y_log10()
plotly::ggplotly(fplt)
```

```{r}
fplt <- disphotic %>%
  ggplot(aes(x = log(depth), y = log(tot_flux_fit), col = profile)) + geom_point() 
plotly::ggplotly(fplt)
```

plot a line on the points deeper than 500m
```{r}
diszoonotic <- disphotic %>% filter(depth > 500)
deepLm <- lm(log(tot_flux_fit) ~ log(depth), data = diszoonotic)
summary(deepLm)
```

```{r}
disphotic %>% filter(depth %in% c(min(depth), max(depth))) %>% group_by(depth) %>% summarize( tot_flux_fit = mean(tot_flux_fit)) %>% mutate(ln_tot_flux = log(tot_flux_fit), ln_depth = log(depth))
```

Its like 1/3 using point slope.