---
title: "R Notebook"
output: html_notebook
---

```{r}
SameGam0 <- gam(TotalParticles ~te(log(lb), log(depth)), offset = log(vol * binsize), family = nb(),
     data = bes %>% filter(project == "ETNP", depth <= 2000))
SameGam0Nl <- gam(TotalParticles ~te(log(lb), (depth)), offset = log(vol * binsize), family = nb(),
     data = bes %>% filter(project == "ETNP", depth <= 2000))
```

```{r}
WBColorMap <- ToPlot%>%
   ggplot(aes(x = lb, y = depth, fill = log10(nnparticles), z = log10(nnparticles))) + geom_tile() + scale_fill_viridis_c(name = expression(log[10](Particles/m^3/mm))) + scale_y_reverse() + scale_x_log10() + geom_contour(color = "black") + geom_hline(yintercept = 160, color = "darkgreen") + geom_hline(yintercept = OMZBase, color = "darkblue") + labs(y = "Depth (m)", x = "Size (mm)") + facet_wrap(~time)
WBColorMap
```

```{r}
WBColorMap <- meanBese%>%
   ggplot(aes(x = lb, y = depth, fill = log10(nnparticles), z = log10(nnparticles))) + geom_tile() + scale_fill_viridis_c(name = expression(log[10](Particles/m^3/mm))) + scale_y_log10() + scale_x_log10() + geom_contour(color = "black") + geom_hline(yintercept = 160, color = "darkgreen") + geom_hline(yintercept = OMZBase, color = "darkblue") + labs(y = "Depth (m)", x = "Size (mm)")
WBColorMap
```

```{r}
pWBPSD <- mbGam %>% ggplot(aes(x = psd, y = depth)) + geom_path() + scale_y_log10()  + geom_hline(yintercept = 160, color = "darkgreen") + geom_hline(yintercept =  OMZBase, color = "darkblue")
pWBPSD
```

Ok. So it turned out that the odd shaped psd distribution was that it was extrapolating PSD into the very negative at low values due to the other points, and those were dragging the average down. 

The plan at this point is to run this smooth for only the two casts of interest




############
## Scratch ##
#############

Link time to profile
```{r}
ProfileTimes <- bds %>% select(profile, time) %>% unique() %>% mutate(time = as.character(time)) %>%
  mutate(time2 = paste(day(time), hour(time), sep = "::")) %>% mutate(time2 = factor(time2, levels = time2))
  
ProfileTimes
```

```{r}
ProfileTimes %>% filter(profile == "stn_043") %>% pull(time)
```


A bunch of upfront smoothing
profile %in% c("stn_032","stn_043")

```{r}
# switched from depth to log depth
# SameGam0 <- gam(TotalParticles ~s(log(lb), log(depth), by = factor(time)), offset = log(vol * binsize), family = nb(),
#     data = bes %>% filter(project == "ETNP", depth <= 2000))
SameGam0 <- gam(TotalParticles ~s(log(lb), log(depth), by = factor(time)), offset = log(vol * binsize), family = nb(),
    data = bes %>% filter(project == "ETNP", depth <= 2000))
SameGam1 <- gam(TotalParticles ~s(log(lb), log(depth * 1000), by = factor(time)), offset = log(vol * binsize), family = nb(),
    data = bes %>% filter(project == "ETNP", depth <= 2000))

```

```{r}
#SameGam <- SameGam1
SameGam <- gam(TotalParticles ~te(log(lb), (depth), k = 7), offset = log(vol * binsize), family = nb(),
    data = bes %>% filter(project == "ETNP", depth <= 2000, profile == "stn_043"))
SameGam <- gam(TotalParticles ~te(log(lb), (depth), k = 7), offset = log(vol * binsize), family = nb(),
    data = bes %>% filter(project == "ETNP", depth <= 2000))
```

```{r}
SameGam <- gam(TotalParticles ~s(log(lb), log(depth)), offset = log(vol * binsize), family = nb(),
    data = bes %>% filter(project == "ETNP", depth <= 2000, profile == "stn_043")) # Looks good!

SameGam <- gam(TotalParticles ~s(log(lb), log(depth)), offset = log(vol * binsize), family = nb(),
    data = bes %>% filter(project == "ETNP", depth <= 2000, profile == "stn_032")) # Looks good!

SameGam <- gam(TotalParticles ~s(log(lb), log(depth), by = factor(time)), offset = log(vol * binsize), family = nb(),
    data = bes %>% filter(project == "ETNP", depth <= 2000, profile %in% c("stn_032", "stn_043")))
```

```{r}
# SameGam <- gam(TotalParticles ~s(log(lb), log(depth)), offset = log(vol * binsize), family = nb(),
#     data = bes %>% filter(project == "ETNP", depth <= 2000, profile == "stn_043")) # Looks good!

SameGam <- gam(TotalParticles ~te(log(lb), log(depth)), offset = log(vol * binsize), family = nb(),
    data = bes %>% filter(project == "ETNP", depth <= 2000, profile == "stn_032")) # Looks good!
```

```{r}
SameGam <- SameGam0
```


```{r}
gam.check(SameGam)
```


```{r}
besE <- bes %>% filter(project == "ETNP")

lb_new <- exp(seq(from = log(0.1), to = log(2.1), by = 0.05))
ub_new <- lead(lb_new)
binsize_new <- ub_new - lb_new

lbbs <- tibble(lb = lb_new, ub = ub_new, binsize = binsize_new)

Expanded <- expand_grid(lb = exp(seq(from = log(0.1), to = log(2), by = 0.05)), depth = seq(from = 20, to = 2000, by = 20), time = as.factor(unique(besE$time))) %>% left_join(lbbs, by = "lb")

Pred <- exp(predict(SameGam, Expanded))
ToPlot <- bind_cols(Expanded, nnparticles = Pred) %>% mutate(time = as.character(time)) %>% mutate(nparticles = nnparticles * binsize) %>%
  left_join(ProfileTimes, by = "time") # put profiles back on
```


Trim off of things that are too deep

```{r}
MaxDepths <- bds %>% group_by(profile) %>% summarise(maxDepth = max(depth))
ToPlot <- ToPlot %>% left_join(MaxDepths) %>% filter(depth <= maxDepth)

```


```{r}
ToPlot %>% filter(lb <= 2,
                  profile == "stn_043") %>%
  ggplot(aes(x = lb, y = depth, fill = log10(nnparticles), z = log10(nnparticles))) + geom_tile() + scale_fill_viridis_c(name = expression(log[10](Particles/m^3/mm))) + scale_y_reverse() + scale_x_log10() + geom_contour(color = "black") + geom_hline(yintercept = 160, color = "darkgreen") + geom_hline(yintercept = OMZBase, color = "darkblue") + labs(y = "Depth (m)", x = "Size (mm)")
```

```{r}
ToPlot %>% filter(lb <= 2,
                  profile == "stn_032") %>%
  ggplot(aes(x = lb, y = depth, fill = log10(nnparticles), z = log10(nnparticles))) + geom_tile() + scale_fill_viridis_c(name = expression(log[10](Particles/m^3/mm))) + scale_y_reverse(limits = c(2000, 0)) + scale_x_log10() + geom_contour(color = "black") + geom_hline(yintercept = 160, color = "darkgreen") + geom_hline(yintercept = OMZBase, color = "darkblue") + labs(y = "Depth (m)", x = "Size (mm)")
```

```{r}
# meanBese <- ToPlot %>% filter(lb <= 2) %>% group_by(lb, depth) %>% summarize(nparticles = mean(nparticles), nnparticles = mean(nnparticles))
# 
# WBColorMap <- meanBese%>%
#    ggplot(aes(x = lb, y = depth, fill = log10(nnparticles), z = log10(nnparticles))) + geom_tile() + scale_fill_viridis_c(name = expression(log[10](Particles/m^3/mm))) + scale_y_reverse() + scale_x_log10() + geom_contour(color = "black") + geom_hline(yintercept = 160, color = "darkgreen") + geom_hline(yintercept = OMZBase, color = "darkblue") + labs(y = "Depth (m)", x = "Size (mm)")
# WBColorMap
```


```{r}
mbGam <- ToPlot %>% group_by(depth, profile)  %>% nest() %>%
  mutate(mod = map(data, ~gam(log(nnparticles) ~ log(lb), family = gaussian(), data = .))) %>% 
  mutate(psd = map_dbl(mod, ~summary(.)$p.coeff[2])) %>%
  left_join(ProfileTimes, by = "profile")
```



## Particle size distribution, smoothed over all stations

```{r}
pWBPSD <- mbGam %>%
  filter(profile %in% c("stn_032", "stn_043")) %>%
  #filter(profile == "stn_043" | depth <= 1000) %>%
  ggplot(aes(x = psd, y = depth, linetype = time2)) + geom_path() + scale_y_reverse()  + geom_hline(yintercept = 160, color = "darkgreen") + geom_hline(yintercept =  OMZBase, color = "darkblue") + scale_linetype_manual(name = "Day::Hour", values = c("dashed", "solid"))
pWBPSD
```



```{r}
pWBPSD <- mbGam %>%
  ggplot(aes(x = psd, y = depth, color = time2)) + geom_path() + scale_y_reverse()  + geom_hline(yintercept = 160, color = "darkgreen") + geom_hline(yintercept =  OMZBase, color = "darkblue")
pWBPSD
```



### Small particles biomass

```{r}
PubDf <- ToPlot %>% mutate(ubiomass = nparticles * lb ^ ag_global) %>% filter(lb < 0.5) %>% group_by(depth, profile) %>% summarize(ubiomass = sum(ubiomass)) %>% ungroup()
photicBiomass <- PubDf %>% filter(depth <= 165, depth >= 155) %>% summarize(ubiomass = mean(ubiomass)) %>% pull(ubiomass)
PubDf <- PubDf %>% mutate(nbiomass = ubiomass/photicBiomass)
PubDf <- PubDf %>% left_join(ProfileTimes, by = "profile")
pWBS <- PubDf %>% filter(profile %in% c("stn_032", "stn_043")) %>%
  ggplot(aes(x = nbiomass, y = depth, linetype = time2)) + geom_path() + scale_y_reverse() + scale_x_continuous(limits = c(0,1.2)) + geom_hline(yintercept = 160, color = "darkgreen") + geom_vline(xintercept = 1, color = "gray50") + geom_vline(xintercept = 0, color = "gray50") + geom_hline(yintercept = OMZBase, color = "darkblue") + labs( x = "Small particle mass (norm.)") + scale_linetype_manual(name = "Day::Hour", values = c("dashed", "solid"))
pWBS
```



## Large Particles Biomass

```{r}
PubDf <- ToPlot %>% mutate(ubiomass = nparticles * lb ^ ag_global) %>% filter(lb >= 0.5) %>% group_by(depth, profile) %>% summarize(ubiomass = sum(ubiomass)) %>% ungroup()
photicBiomass <- PubDf %>% filter(depth <= 165, depth >= 155) %>% summarize(ubiomass = mean(ubiomass)) %>% pull(ubiomass)
PubDf <- PubDf %>% mutate(nbiomass = ubiomass/photicBiomass)
PubDf <- PubDf %>% left_join(ProfileTimes, by = "profile")
pWBS <- PubDf %>% filter(profile %in% c("stn_032", "stn_043")) %>%
  ggplot(aes(x = nbiomass, y = depth, linetype = time2)) + geom_path() + scale_y_reverse() + scale_x_continuous(limits = c(0,1.2)) + geom_hline(yintercept = 160, color = "darkgreen") + geom_vline(xintercept = 1, color = "gray50") + geom_vline(xintercept = 0, color = "gray50") + geom_hline(yintercept = OMZBase, color = "darkblue") + labs( x = "Large particle mass (norm.)") + scale_linetype_manual(name = "Day::Hour", values = c("dashed", "solid"))
pWBS
```


```{r}
LubDf <- ToPlot %>% mutate(ubiomass = nparticles * lb ^ ag_global) %>% filter(lb >= 0.5) %>% group_by(time, depth) %>% summarize(ubiomass = sum(ubiomass)) %>% ungroup %>% group_by(depth)  %>% summarise(ubiomass = mean(ubiomass))
photicBiomass <- LubDf %>% filter(depth <= 165, depth >=155) %>% summarize(ubiomass = mean(ubiomass)) %>% pull(ubiomass)
LubDf <- LubDf %>% mutate(nbiomass = ubiomass/photicBiomass)
pWBL <- LubDf %>% ggplot(aes(x = nbiomass, y = depth)) + geom_path() + scale_y_reverse() + scale_x_continuous(limits = c(0,1)) + geom_hline(yintercept = 160, color = "darkgreen") + labs( x = "Large particle mass (norm.)") + geom_vline(xintercept = 1, color = "gray50") + geom_vline(xintercept = 0, color = "gray50") + geom_hline(yintercept = OMZBase, color = "darkblue")
pWBL
```

