---
# Choose from this list of Journals:
# JGR: Atmospheres, JGR: Biogeosciences, JGR: Earth Surface, 
# JGR: Oceans, JGR: Planets, JGR: Solid Earth, JGR: Space Physics, 
# Global Biogeochemical Cycles, Geophysical Research Letters, 
# Paleoceanography and Paleoclimatology, Radio Science, Reviews of Geophysics, 
# Tectonics, Space Weather, Water Resources Research, Geochemistry, Geophysics, 
# Geosystems, Journal of Advances in Modeling Earth Systems (JAMES),
# Earth's Future, Earth and Space Science, Geohealth
journal: "Global Biogeochemical Cycles"
# Use draft to submit a paper
classoption: "draft,linenumbers"
# A title should be specific, informative, and brief. Use
# abbreviations only if they are defined in the abstract. Titles that
# start with general keywords then specific terms are optimized in
# searches
title: "The title of my paper"
# First name or initial followed by last name
# Authors are individuals who have significantly contributed to the
# research and preparation of the article. Group authors are allowed, if
# each author in the group is separately identified in an appendix.
# Additional author notes should be indicated with
authors:
  - name: Andrew N. Other
    affil: 1
    thanks: Andrew's thanks
  - name: Fred T. Secondauthor
    affil: 1
    thanks: "Current address: Some other place, Germany"
  - name: I. Ken Groupleader
    affil: "1, 2"
affiliations:
  - number: 1
    name: "The first affiliation"
  - number: 2
    name: "The second affiliation"
# More than one corresponding author is allowed in this LaTeX file and for
# publication; but only one corresponding author is allowed in our editorial system.
corresponding_author:
  - name: I. Ken Groupleader
    email: groupleader@fancy.university.com
keypoints:  
  - "List up to three key points (at least one is required)"
  - "Key Points summarize the main points and conclusions of the article"
  - "Each must be 100 characters or less with no special characters or punctuation"
abstract: "A good abstract will begin with a short description of the problem being addressed, briefly describe the new data or analyses, then briefly states the main conclusion(s) and how they are supported and uncertainties."
plain_language_summary: "Some journals require a plain language summary. See: https://publications.agu.org/author-resource-center/text-requirements/#abstract"
output: 
    rticles::agu_article
bibliography: agutest.bib
header-includes: 
      - \usepackage{soulutf8}  # For UTF8 chars in TrackChanges
# AGU recommends using the trackchanges LaTeX package in the edition process
# which is available from this link:
# https://publications.agu.org/files/2019/02/January-14-2019-latex-templates.zip
---

```{r echo=FALSE}
# Some recommended settings. 
knitr::opts_chunk$set(
  echo = FALSE,
  fig.pos = 'h',
  out.extra = "",   # To force the use of figure enviroment
  fig.cap = "Please caption every figure"
)
```

```{r keypoints_check, echo=FALSE, results='asis', eval = TRUE}
# This chunk adds a warning if any keypoint is longer than 100 characters. 
# To disable it, you can remove it or set eval to FALSE.
if (any(nchar(rmarkdown::metadata$keypoints) > 100)) {
  cat("\\textcolor{red}{\\textbf{Warning}: keypoint(s)", 
      knitr::combine_words(which(nchar(rmarkdown::metadata$keypoints) > 100)), 
      "longer than 100 characters.}")
}
```

Suggested section heads

# Introduction

The biological pump, in which sinking particles transport carbon from the surface into the deep ocean, is a key part of the global carbon cycle [@neuerOceanBiologicalCarbon2014; @turnerZooplanktonFecalPellets2015]. Organic matter flux into the deep ocean is a function both of export from the photic zone into the mesopelagic (export flux), and the fraction of that flux that crosses through the mesopelagic (transfer efficiency) [@francoisFactorsControllingFlux2002; @passowBiologicalPumpHigh2012; @siegelPredictionExportFate2016] (Passow and Carlson 2012; Siegel et al. 2016; Francois et al. 2002). The transfer efficiency of the biological pump may affect global atmospheric carbon levels [@kwonImpactRemineralizationDepth2009] (Kwon, Primeau, and Sarmiento 2009). Thus, understanding the processes that shape organic matter degradation in the mesopelagic is critical.

## Test for double add

As seen by [@weberDeepOceanNutrients2016]

# Materials and Methods

Here is text on Materials and Methods.

Do not use bulleted lists; enumerated lists are okay. Use #. for list for a cleaner LaTeX output.

#. First element

#. Second element

[@weberEfficientParticleTransfer2020]

Actual refs
[@evansRoleWaterMasses2020]


## A descriptive heading about methods


# Data

Or section title might be a descriptive heading about data

As of 2018 we recommend use of the TrackChanges package to mark revisions. The trackchanges package adds five new LaTeX commands:

\\note[editor]{The note}

\\annote[editor]{Text to annotate}{The note}

\\add[editor]{Text to add}

\\remove[editor]{Text to remove}

\\change[editor]{Text to remove}{Text to add}

complete documentation is here: http://trackchanges.sourceforge.net/

# Results

Or section title might be a descriptive heading about the results

Enter Figures and Tables near as possible to where they are first mentioned:
DO NOT USE \\psfrag or \\subfigure commands.
DO NOT USE \\newcommand, \\renewcommand, or \\def, etc.

```{r}
plot(pressure)
```

Example table

\begin{table}
 \caption{Time of the Transition Between Phase 1 and Phase 2$^{a}$}
 \centering
 \begin{tabular}{l c}
 \hline
  Run  & Time (min)  \\
 \hline
   $l1$  & 260   \\
   $l2$  & 300   \\
   $l3$  & 340   \\
   $h1$  & 270   \\
   $h2$  & 250   \\
   $h3$  & 380   \\
   $r1$  & 370   \\
   $r2$  & 390   \\
 \hline
 \multicolumn{2}{l}{$^{a}$Footnote text here.}
 \end{tabular}
 \end{table}

AGU prefers the use of {sidewaystable} over {landscapetable} as it causes fewer problems.

```{r, fig.env = "sidewaysfigure"}
plot(pressure)
```

\begin{sidewaystable}
\caption{Caption here}
\label{tab:signif_gap_clos}
\begin{tabular}{ccc}
one&two&three\\
four&five&six
\end{tabular}
\end{sidewaystable}

If using numbered lines, please surround equations with \\begin{linenomath\*}... \\end{linenomath\*}

\begin{linenomath*}
\begin{equation}
y|{f} \sim g(m, \sigma)
\end{equation}
\end{linenomath*}

# Conclusions

\appendix
\section{Here is a sample appendix}

Optional Appendix goes here

Optional Glossary, Notation or Acronym section goes here:

Glossary is only allowed in Reviews of Geophysics

\begin{glossary}
\term{Term}
 Term Definition here
\term{Term}
 Term Definition here
\term{Term}
 Term Definition here
\end{glossary}


\begin{acronyms}
\acro{Acronym}
 Definition here
\acro{EMOS}
 Ensemble model output statistics
\acro{ECMWF}
 Centre for Medium-Range Weather Forecasts
\end{acronyms}

\begin{notation}
\notation{$a+b$} Notation Definition here
\notation{$e=mc^2$}
Equation in German-born physicist Albert Einstein's theory of special
relativity that showed that the increased relativistic mass ($m$) of a
body comes from the energy of motion of the body—that is, its kinetic
energy ($E$)—divided by the speed of light squared ($c^2$).
\end{notation}


\acknowledgments
The acknowledgments must list:
A statement that indicates to the reader where the data
supporting the conclusions can be obtained (for example, in the
references, tables, supporting information, and other databases).

All funding sources related to this work from all authors

Any real or perceived financial conflicts of interests for any author

Other affiliations for any author that may be perceived as having a conflict of 
interest with respect to the results of this paper.

It is also the appropriate place to thank colleagues and other contributors.

AGU does not normally allow dedications. 
